Growing libraries of concepts with wake-sleep program induction

### 2018-07-24 talk.tex
Figure tweaking and more dreams

  \node[latent,scale=1] at (3.5,3) (dx){DSL};
  \node[latent,scale=1] at ([yshift=-1.5cm]dx) (zp){prog};
  \node[obs,scale=1] at ([yshift=-2cm]zp) (xp) {data};
  \node[latent,scale=1] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  %\draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);
%  \node at (nn) {\NeuralNetwork{0.5}};

@@

\begin{frame}{Turtle graphics --- Learning curves and dreams}
  \centering
  \includegraphics[width=9cm]{figures/dreams/montageTalk.eps}
\end{frame}

\begin{frame}{Turtle graphics --- Improved DSL}
  \begin{itemize}
    \item $\frac\pi2$ and $\frac\pi4$ from $\pi$, $2$, $+$ and $/$
    \item A line of length \texttt{n} followed with a right angle
    \item Loops of length \texttt{n} that uses the number \texttt{n} inside.
    \item Unit line then teleport back to origin
    \item ...
  \end{itemize}
\end{frame}

>>>>

  \node[latent,scale=1] at (3.5,3) (dx){DSL};
  \node[latent,scale=1] at ([yshift=-1.5cm]dx) (zp){prog};
  \node[obs,scale=1] at ([yshift=-2cm]zp) (xp) {data};
  \node[latent,scale=1] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  %\draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);
%  \node at (nn) {\NeuralNetwork{0.5}};
  % HACK : "invisible" arrow to phantom and push to the left and align with next
  % slide
  \draw [->,red,opacity=0.0001] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

@@

\begin{frame}{Turtle graphics --- Learning curves}
  \centering
  \includegraphics[width=9cm]{figures/dreams/montageTalkLC.eps}
  \pause{}
  \begin{itemize}
    \item $\frac\pi2$ and $\frac\pi4$ from $\pi$, $2$, $+$ and $/$
    \item A line of length \texttt{n} followed with a right angle
    \item Loops of length \texttt{n} that uses the number \texttt{n} inside.
    \item Unit line then teleport back to origin
    \item ...
  \end{itemize}
\end{frame}

\begin{frame}{Turtle graphics --- Dreams}
  \centering
  \includegraphics[width=7cm]{figures/dreams/montageTalkDreams.eps}
\end{frame}

\begin{frame}{Turtle graphics --- More dreams, 5 minutes, 1st iteration}
  \centering
  \includegraphics[width=8cm]{figures/dreams/5m_firstIteration.eps}
\end{frame}

\begin{frame}{Turtle graphics --- More dreams, 5 minutes, last iteration}
  \centering
  \includegraphics[width=8cm]{figures/dreams/5m_final.eps}
\end{frame}
